---
title: "Reproducing the marine seismic hazard-chain results"
subtitle: "Quantitative Modelling of Marine Seismic Hazard Chains — one document that regenerates every table and figure"
author: "Shi, Hu, Zhang"
date: "`r format(Sys.Date())`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    code_folding: show
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", dpi = 150)
```

# Overview

This single document reproduces **every number and figure** reported in the paper
from the raw cascade tables in `data/`. Knit it (RStudio → *Knit*, or
`rmarkdown::render("reproduce.Rmd")`) to regenerate:

| Output | Section |
|--------|---------|
| Marine network (39 nodes / 152 edges) | \@ref(marine-network) |
| **Table 2** — node in/out degree | \@ref(table-2-node-degrees) |
| **Table 3** — four-layer net flow | \@ref(table-3-four-layer-net-flow) |
| **Table 4** — 15-class marine vs mainland | \@ref(table-4-15-class-comparison) |
| **Table 5 / Sect. 3.5** — directed-edge coverage of the three independent events | \@ref(independent-event-validation) |
| **Table 6 / Sect. 3.5** — conclusions before and after merging the independent events | \@ref(independent-event-validation) |
| **Figure 1** — marine network, in/out degree | \@ref(figure-1) |
| **Figure 2** — marine vs mainland, 15 classes | \@ref(figure-2) |
| **Figure 3 / Sect. 3.4** — robustness & sampling sufficiency | \@ref(figure-3-robustness) |
| **Figure 4 / Sect. 3.5** — three independent events overlaid on the marine network | \@ref(independent-event-validation) |

**Paths are relative** (this file sits at the repository root) and use
`file.path()`, which is correct on Windows, Linux and macOS alike — no per-OS
branching is needed (R also accepts `/` on Windows). The operating system this
run used is printed in the Session information at the end.

```{r libraries}
## Required packages (install once): docxtractr, igraph, dplyr
for (p in c("docxtractr", "igraph", "dplyr"))
  if (!requireNamespace(p, quietly = TRUE))
    stop(sprintf("Please install.packages('%s')", p))
suppressMessages({library(igraph); library(dplyr)})
cat("Running on:", Sys.info()[["sysname"]], "| R", as.character(getRversion()), "\n")
```

```{r paths}
## Relative paths from the repository root (cross-platform via file.path()).
data_dir   <- "data"
marine_f   <- file.path(data_dir, "marine", "tsunami_Dohmen_2025_EQ.docx")
mainland_f <- file.path(data_dir, "mainland_china",
                        paste0("earthquake_table_China_4_", c("E", "N", "SW", "NW"), ".docx"))
stopifnot(file.exists(marine_f), all(file.exists(mainland_f)))
```

# Helper functions

`read_doc()` reads the first table of a `.docx`; the only column used is the
machine-readable **`Proposed Encoding`** field (chains such as
`SEQ,TS;TS,CFL;CFL,PP;`). `build_graph()` turns those encodings into a directed
graph: chains are split on `;`, pairs on `,`, whitespace is trimmed so `" TS"`
and `"TS"` are not treated as different nodes, and the union of all chains is
de-duplicated. **Self-loops are retained** here (one edge, `PP -> PP`, exists in
the record and is part of the 152-edge fine network; it is removed only for the
15-class comparison, exactly as the paper states).

```{r helpers}
read_doc <- function(path) {
  tb <- docxtractr::docx_extract_tbl(docxtractr::read_docx(path), tbl_number = 1)
  as.data.frame(tb, check.names = FALSE)
}

## robustly locate the "Proposed Encoding" column (dot or space in the name)
encoding_of <- function(df) df[[ grep("Encoding", names(df), ignore.case = TRUE)[1] ]]

build_graph <- function(paths) {
  x   <- do.call(rbind, lapply(paths, read_doc))
  enc <- encoding_of(x)
  from <- character(0); to <- character(0)
  for (s in enc) for (seg in strsplit(s, ";")[[1]]) {
    pr <- trimws(strsplit(seg, ",")[[1]])
    if (length(pr) >= 2 && all(nzchar(pr[1:2]))) { from <- c(from, pr[1]); to <- c(to, pr[2]) }
  }
  final <- dplyr::distinct(data.frame(from = from, to = to))  # unique directed edges (self-loops kept)
  igraph::graph_from_data_frame(final, directed = TRUE)
}
```

# Marine network {#marine-network}

The fine marine network is built from `r basename(marine_f)` (366 documented
cascade chains, 39 peril codes).

```{r marine-network}
g_marine <- build_graph(marine_f)
cat(sprintf("Marine fine network: %d nodes, %d directed edges (incl. 1 self-loop PP->PP)\n",
            vcount(g_marine), ecount(g_marine)))
```

# Table 2: node degrees {#table-2-node-degrees}

In/out degree of every node on the **fine** network (self-loop retained, so the
PP self-loop contributes +1 to both PP's in- and out-degree, giving PP = in 9 /
out 1, as in the paper). `net = out − in`.

```{r table-2}
deg_tab <- data.frame(
  Code = V(g_marine)$name,
  In   = degree(g_marine, mode = "in"),
  Out  = degree(g_marine, mode = "out"),
  Net  = degree(g_marine, mode = "out") - degree(g_marine, mode = "in"),
  row.names = NULL)
## the paper's Table 2 lists nodes with in- or out-degree >= 7 (upper quartile)
core <- deg_tab[deg_tab$In >= 7 | deg_tab$Out >= 7, ]
knitr::kable(core[order(-core$Out, -core$In), ], row.names = FALSE,
             caption = "Table 2 — core nodes (in- or out-degree >= 7).")
```

# Table 3: four-layer net flow {#table-3-four-layer-net-flow}

Nodes are aggregated into the four cascade layers; **net flow = out − in** summed
over each layer's members. Expected: **+42 / +1 / −16 / −27** (sums to 0).

```{r table-3}
layer_fine <- c(
  SEQ="Trigger", EQ="Trigger", AS="Trigger", VE="Trigger",
  SLS="Natural", CLS="Natural", LS="Natural", RO="Natural", LB="Natural", SA="Natural",
  LI="Natural", GU="Natural", SUB="Natural", MB="Natural", TS="Natural", CFL="Natural",
  FF="Natural", MED="Natural", WP="Natural", WD="Natural", DI="Natural", FA="Natural",
  PHF="Engineering", SDF="Engineering", SPF="Engineering", SCF="Engineering", NFA="Engineering",
  FI="Engineering", EX="Engineering", CF="Engineering", NF="Engineering",
  MTD="Consequence", BI="Consequence", EC="Consequence", PP="Consequence",
  HD="Consequence", IR="Consequence", SU="Consequence", CP="Consequence")
L4 <- c("Trigger", "Natural", "Engineering", "Consequence")

layer_flow <- function(g, lmap, levels) {
  lay <- factor(lmap[V(g)$name], levels = levels)
  o <- tapply(degree(g, mode = "out"), lay, sum); o[is.na(o)] <- 0
  i <- tapply(degree(g, mode = "in"),  lay, sum); i[is.na(i)] <- 0
  data.frame(Layer = levels, Nodes = as.integer(table(lay)[levels]),
             `Out-flow` = as.integer(o[levels]), `In-flow` = as.integer(i[levels]),
             `Net flow` = as.integer(o[levels] - i[levels]),
             `Net %`   = round((o[levels] - i[levels]) / ecount(g) * 100, 1),
             check.names = FALSE)
}
t3 <- layer_flow(g_marine, layer_fine, L4)
knitr::kable(rbind(t3, data.frame(Layer="Total", Nodes=sum(t3$Nodes),
             `Out-flow`=sum(t3$`Out-flow`), `In-flow`=sum(t3$`In-flow`),
             `Net flow`=sum(t3$`Net flow`), `Net %`=round(sum(t3$`Net %`),1), check.names=FALSE)),
             row.names = FALSE, caption = "Table 3 — four-layer net flow (fine network).")
```

# Table 4: 15-class comparison {#table-4-15-class-comparison}

Both chains are reduced to the **same 15 classes** and **simplified (duplicate
edges and self-loops removed)** before any metric is computed. The 39 → 15
mapping (also given in the paper's appendix) is:

```{r coarse-map}
coarse_map <- c(
  SEQ="EQ or AS", AS="EQ or AS", EQ="EQ or AS", VE="EQ or AS",
  GU="Mass Slide", SLS="Mass Slide", CLS="Mass Slide", LI="Mass Slide", MB="Mass Slide",
  SUB="Mass Slide", LS="Mass Slide", RO="Mass Slide", LB="Mass Slide", SA="Mass Slide",
  PHF="Critical Infra. Fail.", SDF="Critical Infra. Fail.", CF="Critical Infra. Fail.",
  NFA="Critical Infra. Fail.", SPF="Critical Infra. Fail.",
  BI="Business Interr.", MTD="Business Interr.", WP="Water Dil.", WD="Water Dil.",
  NF="Critical NET Fail.", SCF="Critical NET Fail.", FA="Flora an Fauna", MED="Flora an Fauna",
  FI="Fire", EX="Fire", IR="Healthcare Deg.", HD="Healthcare Deg.",
  TS="Flood", CFL="Flood", FF="Flood",
  EC="Econ. Crisis", DI="Disease", PP="Phy.-Psych. Trauma", CP="Culture Perils", SU="Social Unrest")
stopifnot(length(setdiff(V(g_marine)$name, names(coarse_map))) == 0)  # every marine node is mapped
```

```{r build-coarse}
## contract the fine marine graph to 15 classes; mainland is already 15-class
grp <- factor(coarse_map[V(g_marine)$name])
g_marine_c <- contract(g_marine, as.integer(grp), vertex.attr.comb = "first")
V(g_marine_c)$name <- levels(grp)
g_marine_c   <- simplify(g_marine_c, remove.multiple = TRUE, remove.loops = TRUE)  # -> 57 edges

g_mainland   <- build_graph(mainland_f)
g_mainland_c <- simplify(g_mainland, remove.multiple = TRUE, remove.loops = TRUE)  # -> 47 edges
```

The full Table 4 — comparable topology metrics **and** the four-layer net flow,
combined in one table (Marine vs Mainland), exactly as in the paper.
**Out/in-degree centralisation uses the paper's Eq. (15)**,
`sum(d_max − d_i) / (N−1)^2` (identical to `igraph::centr_degree` once self-loops
are removed).

```{r table-4}
## out/in-degree centralisation, paper Eq. (15): sum(d_max - d_i) / (N-1)^2
Cfree <- function(g, mode) { d <- degree(g, mode = mode); N <- vcount(g)
  sum(max(d) - d) / ((N - 1)^2) }

## 15-class -> four-layer map, for the net-flow rows
layer15 <- c("EQ or AS"="Trigger",
  "Mass Slide"="Natural","Water Dil."="Natural","Flora an Fauna"="Natural","Flood"="Natural","Disease"="Natural",
  "Critical Infra. Fail."="Engineering","Critical NET Fail."="Engineering","Fire"="Engineering",
  "Business Interr."="Consequence","Healthcare Deg."="Consequence","Econ. Crisis"="Consequence",
  "Phy.-Psych. Trauma"="Consequence","Culture Perils"="Consequence","Social Unrest"="Consequence")

## every reported Table 4 value for one 15-class graph, as a labelled character column
table4_col <- function(g) {
  nf <- layer_flow(g, layer15, L4)$`Net %`          # Trigger / Natural / Engineering / Consequence
  c(`Nodes / edges`             = sprintf("%d / %d", vcount(g), ecount(g)),
    `Network density`           = sprintf("%.3f", edge_density(g, loops = FALSE)),
    `Out-degree centralisation` = sprintf("%.3f", Cfree(g, "out")),
    `In-degree centralisation`  = sprintf("%.3f", Cfree(g, "in")),
    `Max out-degree`            = sprintf("%d",   max(degree(g, mode = "out"))),
    `Pure sources / sinks`      = sprintf("%d / %d", sum(degree(g, mode="in")==0),
                                                     sum(degree(g, mode="out")==0)),
    `Mean path length`          = sprintf("%.2f", mean_distance(g, directed = TRUE)),
    `Net flow — Trigger`        = sprintf("%+.1f%%", nf[1]),
    `Net flow — Natural`        = sprintf("%+.1f%%", nf[2]),
    `Net flow — Engineering`    = sprintf("%+.1f%%", nf[3]),
    `Net flow — Consequence`    = sprintf("%+.1f%%", nf[4]))
}
marine_col   <- table4_col(g_marine_c)
mainland_col <- table4_col(g_mainland_c)
knitr::kable(data.frame(Metric = names(marine_col),
                        `Marine (15 classes)` = unname(marine_col),
                        `Mainland`            = unname(mainland_col),
                        check.names = FALSE),
             row.names = FALSE,
             caption = "Table 4 — 15-class comparison: topology metrics and four-layer net flow.")
```

# Chain-breaking / mitigation leverage {#chain-breaking}

**What it shows / why:** the Discussion measures each node's leverage by the
*cascade reach* it carries, that is the number of ordered peril pairs still
joined by a directed path (equivalently, the sum over perils of how many
downstream perils each one can reach). Deleting a node and recomputing the
reach gives the share it carries; a greedy search, with the uncontrollable
seismic sources excluded, finds the most disruptive combination. This
reproduces the 619 / 409 / 239 reach figures and the 34 / 14 / 13 / 61 %
reductions reported in the Discussion.

```{r chain-breaking}
gr    <- simplify(g_marine, remove.loops = TRUE, remove.multiple = TRUE)  # reachability ignores self-loops
reach <- function(g) if (vcount(g) == 0) 0L else
  sum(vapply(seq_len(vcount(g)), function(i) length(subcomponent(g, i, mode = "out")) - 1L, integer(1)))
dropR <- function(nodes) reach(delete_vertices(gr, intersect(nodes, V(gr)$name)))
R0 <- reach(gr)
cat(sprintf("baseline cascade reach R0 = %d  (%d nodes, %d edges)\n", R0, vcount(gr), ecount(gr)))

## single-node removals. CF 34 %, TS 14 %, NF 13 % are the Discussion figures; fire (FI)
## is added to show it cuts more reach than NF despite fewer neighbours (degree != cut power)
distinct_nb <- function(n) length(union(as_ids(neighbors(gr, n, mode = "in")),
                                        as_ids(neighbors(gr, n, mode = "out"))))
single <- data.frame(node = c("CF", "TS", "NF", "FI"))
single$neighbours  <- vapply(single$node, distinct_nb, integer(1))
single$reach_after <- vapply(single$node, dropR, integer(1))
single$reduction   <- sprintf("%.1f%%", 100 * (R0 - single$reach_after) / R0)
knitr::kable(single, row.names = FALSE,
             caption = "Single-node removal: distinct neighbours, cascade reach after removal, and reduction from R0. Fire (FI, 14.7 %) cuts more reach than critical network failure (NF, 12.8 %) despite fewer neighbours, since the ranking reflects directed reachability, not node degree.")

## greedy search for the 3 most disruptive nodes, excluding the seismic sources SEQ, EQ
pool <- setdiff(V(gr)$name, c("SEQ", "EQ")); chosen <- character(0)
for (s in 1:3) {
  cand    <- setdiff(pool, chosen)
  reaches <- vapply(cand, function(n) dropR(c(chosen, n)), integer(1))
  chosen  <- c(chosen, cand[which.min(reaches)])
  cat(sprintf("greedy step %d: add %-3s -> cumulative reach reduction %.1f%%\n",
              s, chosen[s], 100 * (R0 - min(reaches)) / R0))
}
cat(sprintf("optimal set {%s}: reach %d -> %d, reduction %.1f%%\n",
            paste(chosen, collapse = ", "), R0, dropR(chosen), 100 * (R0 - dropR(chosen)) / R0))

## why fire enters ahead of network failure at step 2 (marginal cut after CF is already gone)
R_CF <- dropR("CF")
cat(sprintf("step-2 marginal after removing CF: FI cuts %d further pairs vs NF %d -- fire wins despite fewer neighbours\n",
            R_CF - dropR(c("CF", "FI")), R_CF - dropR(c("CF", "NF"))))
```

# Figure 1 {#figure-1}

**What it shows / how it is made:** the fine 39-node marine network, drawn twice
with a shared force-directed layout (`igraph::layout_with_fr`, `set.seed(123)`
for reproducibility). Node **colour and size encode degree** on a yellow→red
scale; panel (a) uses in-degree, panel (b) out-degree (zero-out-degree nodes
white). This is the code behind the paper's `fig01.png`.

```{r figure-1, fig.width=13, fig.height=6.2}
pal <- colorRampPalette(c("#FFF886", "#d21d13"))
plot_deg <- function(g, layout, metric, zero_white = FALSE) {
  m <- metric / max(metric)
  col <- pal(500)[as.numeric(cut(m, breaks = 500))]; if (zero_white) col[metric == 0] <- "white"
  s <- sqrt(metric); vs <- 4 + (if (max(s)==0) 0 else s/max(s)) * 14
  plot(g, layout = layout, vertex.size = vs, vertex.color = col,
       vertex.frame.color = adjustcolor("grey30", .5),
       vertex.label = V(g)$name, vertex.label.family = "sans",
       vertex.label.color = "black", vertex.label.cex = .8, vertex.label.font = 2,
       edge.arrow.size = .35, edge.width = .6, edge.curved = .15,
       edge.color = adjustcolor("grey60", .45))
}
## helper: write a 300-dpi TIFF (LZW) and optionally a PNG of a plot, then draw it inline
export_fig <- function(plotfun, base, w, h) {
  dir.create("figures", showWarnings = FALSE)
  ## 300-dpi PNG
  png(file.path("figures", paste0(base, "_300dpi.png")),
      width = w, height = h, units = "in", res = 300)
  plotfun(); invisible(dev.off())
  ## 300-dpi TIFF (LZW)
  tiff(file.path("figures", paste0(base, "_300dpi.tif")),
       width = w, height = h, units = "in", res = 300, compression = "lzw")
  plotfun(); invisible(dev.off())
  plotfun()   # inline for the knitted HTML
}
set.seed(123); lay1 <- layout_with_fr(g_marine, niter = 3000)
draw_fig1 <- function() {
  par(mfrow = c(1, 2), mar = c(0, 0, 2, 0))
  plot_deg(g_marine, lay1, degree(g_marine, mode = "in"));  title("(a) in-degree")
  plot_deg(g_marine, lay1, degree(g_marine, mode = "out"), zero_white = TRUE); title("(b) out-degree")
}
export_fig(draw_fig1, "fig01", 13, 6.2)
```

# Figure 2 {#figure-2}

**What it shows / how it is made:** the marine (15 classes) and mainland (15
classes) networks on **one shared force-directed layout** so each class sits in
the same place across panels. Four panels: marine in/out degree, mainland in/out
degree; colour and size encode degree. This is the code behind `fig02a.png`.

```{r figure-2, fig.width=12, fig.height=11}
abbr <- c("EQ or AS"="EQ","Mass Slide"="MS","Critical Infra. Fail."="CIF","Business Interr."="BI",
  "Water Dil."="WD","Critical NET Fail."="CNF","Flora an Fauna"="FA","Fire"="FI",
  "Healthcare Deg."="HD","Flood"="FL","Econ. Crisis"="EC","Disease"="DI",
  "Phy.-Psych. Trauma"="PP","Culture Perils"="CP","Social Unrest"="SU")
common <- sort(unique(c(V(g_marine_c)$name, V(g_mainland_c)$name)))
uni <- graph_from_data_frame(
  rbind(igraph::as_data_frame(g_marine_c), igraph::as_data_frame(g_mainland_c)),
  directed = TRUE, vertices = data.frame(name = common))
set.seed(123); lay2 <- layout_with_fr(uni, niter = 3000); rownames(lay2) <- V(uni)$name
panel <- function(g, mode, ttl) {
  m <- degree(g, mode = mode); mm <- if (max(m)==0) m else m/max(m)
  col <- pal(500)[as.numeric(cut(mm, breaks = 500))]; if (mode=="out") col[m==0] <- "white"
  s <- sqrt(m); vs <- 12 + (if (max(s)==0) 0 else s/max(s)) * 26
  plot(g, layout = lay2[V(g)$name, ], vertex.size = vs, vertex.color = col,
       vertex.frame.color = adjustcolor("grey30", .5), vertex.label = abbr[V(g)$name],vertex.label.family = "sans",
       vertex.label.color = "black", vertex.label.cex = 1.4, vertex.label.font = 2,
       edge.color = adjustcolor("grey60", .5), edge.width = .7, edge.arrow.size = .35,
       edge.curved = .15, main = ttl)
}
draw_fig2 <- function() {
  par(mfrow = c(2, 2), mar = c(1, 1, 2.5, 1))
  panel(g_marine_c, "in", "(a) Marine — in-degree");    panel(g_marine_c, "out", "(b) Marine — out-degree")
  panel(g_mainland_c, "in", "(c) Mainland — in-degree"); panel(g_mainland_c, "out", "(d) Mainland — out-degree")
}
export_fig(draw_fig2, "fig02", 12, 11)
```

# Figure 3 / Sect. 3.4: robustness & sampling sufficiency {#figure-3-robustness}

**What it shows / how it is made:** the 366 chains cluster under **58 source
events (tsunamis)**, so all resampling is at the **event level** (cluster
bootstrap). Panel (a) is the edge-accumulation (sampling-sufficiency) curve;
panel (b) is the fraction of `B=1000` event-bootstrap resamples in which each
qualitative conclusion holds (C1 pure sources; C2 dominant hubs SEQ/CF; C3
NF-as-convergence; C4 monotone four-layer cascade).

```{r robustness, fig.width=10, fig.height=4.2}
set.seed(1)
x <- read_doc(marine_f)
id <- x[[ grep("^ID$|ID", names(x))[1] ]]; enc <- encoding_of(x)
cur <- NA; ev <- character(length(enc))                     # forward-fill event id
for (i in seq_along(enc)) { if (!is.na(id[i]) && nzchar(trimws(id[i]))) cur <- id[i]; ev[i] <- cur }
chain_edges <- lapply(seq_along(enc), function(i) {
  e <- character(0)
  for (seg in strsplit(enc[i], ";")[[1]]) { pr <- trimws(strsplit(seg, ",")[[1]])
    if (length(pr) >= 2 && all(nzchar(pr[1:2]))) e <- c(e, paste(pr[1], pr[2], sep = "|")) }
  unique(e) })
events   <- unique(ev)
ev_edges <- lapply(events, function(g) unique(unlist(chain_edges[ev == g])))
n_ev <- length(events); full <- length(unique(unlist(ev_edges)))
efreq <- table(unlist(ev_edges))

build_e  <- function(edges) { ee <- do.call(rbind, strsplit(edges, "\\|"))
  graph_from_data_frame(data.frame(from = ee[,1], to = ee[,2]), directed = TRUE) }
concl <- function(g) { dout <- degree(g, mode="out"); din <- degree(g, mode="in")
  nm <- V(g)$name; gv <- function(v,d) if (v%in%nm) d[v] else 0
  L <- layer_fine[nm]; nf <- sapply(L4, function(k) sum(dout[L==k]) - sum(din[L==k]))
  c(C1 = setequal(nm[din==0], c("SEQ","EQ")),
    C2 = (names(which.max(dout))=="SEQ" && names(which.max(din))=="CF"),
    C3 = (gv("NF",din) > gv("NF",dout)),
    C4 = (nf["Trigger"]>nf["Natural"] && nf["Natural"]>nf["Engineering"] &&
          nf["Engineering"]>nf["Consequence"] && nf["Trigger"]>0 && nf["Consequence"]<0)) }

B <- 1000
stab <- rowMeans(sapply(1:B, function(b)
  concl(build_e(unique(unlist(ev_edges[sample(n_ev, n_ev, replace = TRUE)])))))) * 100
fr  <- seq(.05, 1, .05)
acc <- sapply(fr, function(f) { k <- max(1, round(f*n_ev))
  mean(sapply(1:200, function(s) length(unique(unlist(ev_edges[sample(n_ev, k)]))))) })
fold <- sample(rep(1:5, length.out = n_ev))
core_cov <- mean(sapply(1:5, function(f) { tr <- unique(unlist(ev_edges[fold!=f]))
  te <- intersect(names(efreq)[efreq>=2], unique(unlist(ev_edges[fold==f])))
  if (length(te)==0) NA else 100*sum(te %in% tr)/length(te) }), na.rm = TRUE)

draw_fig3 <- function() {
  par(mfrow = c(1, 2), mar = c(4.2, 4.2, 2.4, 1))
  plot(100*fr, 100*acc/full, type = "o", pch = 19, col = "#d21d13", ylim = c(0,100),
       xlab = "Source events (tsunamis) used (%)", ylab = "Unique edges recovered (%)",
       main = "(a) Sampling sufficiency")
  abline(h = core_cov, lty = 2, col = "grey40")
  barplot(stab, col = "#F2A43A", ylim = c(0,100), names.arg = c("C1","C2","C3","C4"),
          ylab = "Holds in resamples (%)", main = "(b) Conclusion stability (event bootstrap)")
  abline(h = 95, lty = 2, col = "grey40")
}
export_fig(draw_fig3, "fig03", 10, 4.2)
cat(sprintf("events=%d | C1..C4 hold in %s%% | core edges recovered out-of-sample: %.1f%%\n",
            n_ev, paste(round(stab), collapse="/"), core_cov))
```

# Independent-event validation {#independent-event-validation}

**What it shows / why:** three major submarine-earthquake tsunamis that are **absent
from the paper's record** — the 2004 Indian Ocean (Sumatra-Andaman), the 1960
Valdivia (Chile) and the 2018 Palu (Sulawesi) events — are encoded as documented,
individually sourced cascade chains in
`data/marine/tsunami_extra_events_2004_1960_2018_EQ.docx` (a `Source` column, ignored
by the analysis, carries the provenance). This section (1) draws the three events on
their own, (2) overlays them on the paper's network, and (3) tests whether the paper's
conclusions survive the new data.

## The three events on their own

```{r extra-network, fig.width=13, fig.height=6.2}
extra_f <- file.path(data_dir, "marine", "tsunami_extra_events_2004_1960_2018_EQ.docx")
g_extra <- build_graph(extra_f)
cat(sprintf("Extra-events network: %d nodes, %d directed edges\n", vcount(g_extra), ecount(g_extra)))
set.seed(123); layE <- layout_with_fr(g_extra, niter = 3000)
par(mfrow = c(1, 2), mar = c(0, 0, 2, 0))
plot_deg(g_extra, layE, degree(g_extra, mode = "in"));  title("(a) in-degree")
plot_deg(g_extra, layE, degree(g_extra, mode = "out"), zero_white = TRUE); title("(b) out-degree")
```

## Old versus new dataset size

```{r dataset-sizes}
noloop <- function(g) ecount(simplify(g, remove.loops = TRUE, remove.multiple = FALSE))
meta <- function(path) {
  x <- read_doc(path); id <- x[[1]]; en <- encoding_of(x)
  cur <- NA; ev <- character(nrow(x)); nch <- 0L
  for (i in seq_len(nrow(x))) {
    if (!is.na(id[i]) && trimws(id[i]) != "") cur <- trimws(id[i])
    ev[i] <- cur
    if (!is.na(en[i]) && nzchar(trimws(en[i]))) nch <- nch + 1L
  }
  c(events = length(unique(ev)), chains = nch)
}
mo <- meta(marine_f); me <- meta(extra_f)
knitr::kable(data.frame(
  Dataset = c("Old (tsunami_Dohmen_2025_EQ)", "New (three extra events)"),
  Events  = c(mo[["events"]], me[["events"]]),
  Chains  = c(mo[["chains"]], me[["chains"]]),
  Nodes   = c(vcount(g_marine), vcount(g_extra)),
  `Edges (incl. self-loop)` = c(ecount(g_marine), ecount(g_extra)),
  `Edges (no self-loop)`    = c(noloop(g_marine), noloop(g_extra)),
  check.names = FALSE),
  row.names = FALSE, caption = "Node and edge counts of the old and new datasets.")
```

## The three events overlaid on the paper's network

New-event **nodes are coloured by layer** and their **labels are black**. Among the
edges the three events contribute, the **14 links absent from the paper's record are
drawn in dark red**, the remaining new-event edges (already documented) in black, and
every node, edge and label that comes only from the original network in grey. The
dark-red edges are exactly the enrichment the new events add; the black-and-coloured
footprint is what they reconfirm in the paper's structure.

```{r extra-overlay, fig.width=11, fig.height=9.5}
lay_col <- c(Trigger = "#e4572e", Natural = "#2a9d8f",
             Engineering = "#e9a220", Consequence = "#4a6fa5")
E_orig  <- igraph::as_data_frame(g_marine)
E_extra <- igraph::as_data_frame(g_extra)
g_union <- graph_from_data_frame(unique(rbind(E_orig, E_extra)), directed = TRUE)

new_nodes <- V(g_extra)$name
new_ekey  <- paste(E_extra$from, E_extra$to)
ekey_union <- with(igraph::as_data_frame(g_union), paste(from, to))
old_ekey   <- paste(E_orig$from, E_orig$to)
is_new_e   <- ekey_union %in% new_ekey
is_novel_e <- is_new_e & !(ekey_union %in% old_ekey)   # the 14 links absent from the record
is_new_v   <- V(g_union)$name %in% new_nodes

vcol  <- ifelse(is_new_v, lay_col[layer_fine[V(g_union)$name]], "grey88")
vlcol <- ifelse(is_new_v, "black", "grey70")
ecol  <- ifelse(is_novel_e, "#8b0000", ifelse(is_new_e, "black", adjustcolor("grey40", .8)))
ewid  <- ifelse(is_novel_e, 2.4, ifelse(is_new_e, 1.3, .5))

set.seed(123); layU <- layout_with_fr(g_union, niter = 3000)
draw_overlay <- function() {
  par(mar = c(0, 0, 0, 0))
  plot(g_union, layout = layU,
       vertex.size = 7, vertex.color = vcol, vertex.frame.color = adjustcolor("grey40", .5),
       vertex.label = V(g_union)$name, vertex.label.family = "sans",
       vertex.label.color = vlcol, vertex.label.cex = .8, vertex.label.font = 2,
       edge.color = ecol, edge.width = ewid, edge.arrow.size = .3, edge.curved = .12)
  legend("bottomleft", legend = names(lay_col), col = lay_col, pch = 19, bty = "n",
         cex = 1.0, title = "New-event nodes (by layer)")
  legend("bottomright",
         legend = c("novel edge (14; new only)", "new-event edge (also in record)", "original-only edge"),
         col = c("#8b0000", "black", "grey40"), lwd = c(2.4, 1.3, .8), bty = "n", cex = 1.0)
}
## save standalone 300-dpi TIFF + PNG (publication quality), then render inline below
export_fig(draw_overlay, "fig04_overlay_events", 11, 9.5)
```

## Do the conclusions survive the new data?

```{r extra-validation}
selfless <- function(df) df[df$from != df$to, , drop = FALSE]
orig_keys <- with(selfless(igraph::as_data_frame(g_marine)), paste(from, to))

## (A) directed-edge coverage, per event and combined
xx <- read_doc(extra_f); enc <- encoding_of(xx); id <- xx[[1]]
cur <- NA; ev <- character(nrow(xx))
for (i in seq_len(nrow(xx))) { if (!is.na(id[i]) && trimws(id[i]) != "") cur <- trimws(id[i]); ev[i] <- cur }
edges_of <- function(s) {
  e <- c(); for (p in strsplit(s, ";")[[1]]) { pr <- trimws(strsplit(p, ",")[[1]])
    if (length(pr) >= 2 && all(nzchar(pr[1:2])) && pr[1] != pr[2]) e <- c(e, paste(pr[1], pr[2])) }
  unique(e)
}
covA <- do.call(rbind, lapply(unique(ev), function(g) {
  ek <- unique(unlist(lapply(enc[ev == g], edges_of)))
  data.frame(Event = g, Links = length(ek), `In network` = sum(ek %in% orig_keys),
             Coverage = sprintf("%.0f%%", 100 * mean(ek %in% orig_keys)), check.names = FALSE) }))
all_ek <- unique(unlist(lapply(enc, edges_of)))
covA <- rbind(covA, data.frame(Event = "ALL THREE", Links = length(all_ek),
              `In network` = sum(all_ek %in% orig_keys),
              Coverage = sprintf("%.0f%%", 100 * mean(all_ek %in% orig_keys)), check.names = FALSE))
knitr::kable(covA, row.names = FALSE,
             caption = sprintf("(A) Directed-edge coverage of the three independent events by the paper's network (%d novel enrichment links).",
                               sum(!all_ek %in% orig_keys)))

## (B) conclusion stability on original vs augmented network
check <- function(g) {
  g <- simplify(g, remove.multiple = TRUE, remove.loops = TRUE)
  nm <- V(g)$name; ind <- degree(g, mode = "in"); outd <- degree(g, mode = "out"); lv <- layer_fine[nm]
  net <- sapply(L4, function(k) sum(outd[lv == k]) - sum(ind[lv == k]))
  list(N = vcount(g), E = ecount(g), src = sort(nm[ind == 0]),
       to = nm[which.max(outd)], tov = max(outd), ti = nm[which.max(ind)], tiv = max(ind),
       nfi = ind[nm == "NF"], nfo = outd[nm == "NF"], net = net,
       C1 = setequal(nm[ind == 0], c("SEQ", "EQ")),
       C2 = (nm[which.max(outd)] == "SEQ" && nm[which.max(ind)] == "CF"),
       C3 = (ind[nm == "NF"] > outd[nm == "NF"]),
       C4 = (net[["Trigger"]] > net[["Natural"]] && net[["Natural"]] > net[["Engineering"]] &&
             net[["Engineering"]] > net[["Consequence"]] && net[["Trigger"]] > 0 && net[["Consequence"]] < 0))
}
g_aug <- graph_from_data_frame(unique(rbind(E_orig, E_extra)), directed = TRUE)
b0 <- check(g_marine); b1 <- check(g_aug)
fmt <- function(b) c(sprintf("%d / %d", b$N, b$E), paste(b$src, collapse = ", "),
  sprintf("%s (%d)", b$to, b$tov), sprintf("%s (%d)", b$ti, b$tiv), sprintf("%d / %d", b$nfi, b$nfo),
  sprintf("%+d / %+d / %+d / %+d", b$net[["Trigger"]], b$net[["Natural"]], b$net[["Engineering"]], b$net[["Consequence"]]),
  b$C1, b$C2, b$C3, b$C4)
tabB <- data.frame(Quantity = c("Nodes / edges", "Pure sources", "Top out-degree", "Top in-degree",
  "NF in / out", "Layer net flow T/N/E/C", "C1 sources are only SEQ,EQ",
  "C2 SEQ out-hub & CF in-hub", "C3 NF is convergence node", "C4 monotone four-layer cascade"),
  `Original (58 events)` = fmt(b0), `Augmented (61 events)` = fmt(b1), check.names = FALSE)
knitr::kable(tabB, row.names = FALSE,
             caption = "(B) Core conclusions before and after merging the three independent events.")

## (C) node-importance rank stability (Spearman)
cm <- intersect(V(g_marine)$name, V(g_aug)$name)
so <- cor(degree(g_marine, mode = "out")[cm], degree(g_aug, mode = "out")[cm], method = "spearman")
si <- cor(degree(g_marine, mode = "in")[cm],  degree(g_aug, mode = "in")[cm],  method = "spearman")
knitr::kable(data.frame(Metric = c("Out-degree ranking", "In-degree ranking"),
  `Spearman (orig vs augmented)` = sprintf("%.3f", c(so, si)), check.names = FALSE),
  row.names = FALSE, caption = "(C) Node-importance rank stability under the new data.")
```

# Interactive viewer data {#viewer-data}

**What it makes / why:** the interactive network viewer linked from the figure
captions (`docs/index.html`, served at
<https://hazardchain.github.io/NHESS-marine-seismic-hazard-chains-code-data/>) is driven
by `docs/graph-data.js`. This chunk regenerates that file **from the very same
graph objects** used for the tables and figures above (`g_marine`,
`g_marine_c`, `g_mainland_c`), so the web page, the paper figures, and the
tables are guaranteed to be one and the same network — no hand-maintained copy
can drift. `jsonlite` ships with `rmarkdown`, so knitting this document already
provides it. The only extra input is the human-readable peril names used for
the tooltips.

```{r viewer-data}
## full peril names for the 39 fine nodes (viewer tooltips only; no metric uses them)
full_name_fine <- c(
  SEQ="Submarine Earthquake", EQ="Coastal Earthquake", AS="Aftershock", VE="Volcanic Eruption",
  SLS="Submarine Landslide", CLS="Coastal Landslide", LS="Landslide", RO="Rockfall", LB="Lake Burst",
  SA="Snow Avalanche", LI="Liquefaction", GU="Ground Uplift", SUB="Subsidence", MB="Methane Blowout",
  TS="Tsunami", CFL="Coastal Flooding", FF="Fluvial Flood", MED="Marine Ecosystem Damage",
  WP="Water Pollution", WD="Water Dilemma", DI="Disease", FA="Flora and Fauna",
  PHF="Port / Harbour Failure", SDF="Seawall / Dike Failure", SPF="Subsea Pipeline Failure",
  SCF="Subsea Cable Failure", NFA="Nuclear Facility Accident", FI="Fire", EX="Explosion",
  CF="Critical Infrastructure Failure", NF="Critical Network Failure",
  MTD="Maritime Transport Disruption", BI="Business Interruption", EC="Economic Crisis",
  PP="Physical & Psychological Trauma", HD="Healthcare Degradation", IR="Insufficient Rescue",
  SU="Social Unrest", CP="Culture Perils")
stopifnot(setequal(names(full_name_fine), V(g_marine)$name))  # every fine node has a name

ident <- function(g) { n <- V(g)$name; setNames(n, n) }
mk_nodes <- function(g, label, full, layer) {
  nm <- V(g)$name
  df <- data.frame(id = nm, label = unname(label[nm]), full = unname(full[nm]),
                   layer = unname(layer[nm]),
                   `in`  = as.integer(degree(g, mode = "in")),
                   out   = as.integer(degree(g, mode = "out")),
                   check.names = FALSE, stringsAsFactors = FALSE)
  df[order(df$id), , drop = FALSE]                 # deterministic order (platform-independent)
}
mk_edges <- function(g) { e <- igraph::as_data_frame(g)[, c("from", "to")]
  e[order(e$from, e$to), , drop = FALSE] }

## overlay: union of the original network and the three independent events;
## per-node "isNew" flag (touched by a new event) and per-edge category
## (novel = in the new events only; new = in both; old = original only).
mk_nodes_overlay <- function(g) {
  nm <- V(g)$name
  data.frame(id = nm, label = nm, full = unname(full_name_fine[nm]),
             layer = unname(layer_fine[nm]),
             `in`  = as.integer(degree(g, mode = "in")),
             out   = as.integer(degree(g, mode = "out")),
             isNew = nm %in% new_nodes,
             check.names = FALSE, stringsAsFactors = FALSE)[order(nm), , drop = FALSE]
}
mk_edges_overlay <- function(g) {
  e <- igraph::as_data_frame(g)[, c("from", "to")]
  k <- paste(e$from, e$to); isN <- k %in% new_ekey; isO <- k %in% old_ekey
  e$cat <- ifelse(isN & !isO, "novel", ifelse(isN & isO, "new", "old"))
  e[order(e$from, e$to), , drop = FALSE]
}

GRAPHS <- list(
  fig1       = list(nodes = mk_nodes(g_marine,     ident(g_marine),     full_name_fine,     layer_fine),
                    edges = mk_edges(g_marine)),
  marine15   = list(nodes = mk_nodes(g_marine_c,   abbr, ident(g_marine_c),   layer15),
                    edges = mk_edges(g_marine_c)),
  mainland15 = list(nodes = mk_nodes(g_mainland_c, abbr, ident(g_mainland_c), layer15),
                    edges = mk_edges(g_mainland_c)),
  overlay    = list(nodes = mk_nodes_overlay(g_union), edges = mk_edges_overlay(g_union)))

if (!requireNamespace("jsonlite", quietly = TRUE)) {
  message("jsonlite not available; skipping docs/graph-data.js regeneration.")
} else if (dir.exists("docs")) {
  js <- paste0(
    "// Auto-generated by reproduce.Rmd from the docx sources in data/. Do not edit by hand.\n",
    "const GRAPHS = ", jsonlite::toJSON(GRAPHS, auto_unbox = TRUE, pretty = TRUE), ";\n")
  writeLines(js, file.path("docs", "graph-data.js"))
  cat(sprintf("Wrote docs/graph-data.js  |  fig1 %d/%d, marine15 %d/%d, mainland15 %d/%d, overlay %d/%d (nodes/edges)\n",
    nrow(GRAPHS$fig1$nodes),       nrow(GRAPHS$fig1$edges),
    nrow(GRAPHS$marine15$nodes),   nrow(GRAPHS$marine15$edges),
    nrow(GRAPHS$mainland15$nodes), nrow(GRAPHS$mainland15$edges),
    nrow(GRAPHS$overlay$nodes),    nrow(GRAPHS$overlay$edges)))
} else {
  message("docs/ folder not found next to reproduce.Rmd; skipping viewer regeneration.")
}
```

The web viewer therefore shares its single source of truth with Figs 1–2 and
Tables 2–4: re-knit this document and the interactive page updates automatically.

# Session information

```{r session}
cat("OS:", Sys.info()[["sysname"]], Sys.info()[["release"]], "\n")
sessionInfo()
```
